Data Pre-Processing/Cleaning Script

### 2023-02-24 code/processing_code/processingfile_v1.qmd
part 2 stuff

---
title: "Data Pre-Processing/Cleaning Script"
author: "Andreas Handel"
date: "2023-01-03"
output: html_document
---

# Load Libraries
```{r}
# General Pre-Processing
library(tidyverse)
library(dplyr)
library(stringr)

@@

```{r}
# Plot of NAs After Limiting to Analysis Data to Food
plot_na_pareto(analysis_data %>% filter(`Primary Mode` == "Food"))
```
## Checking Etiologies
```{r}
# Training Data
unique(training_data$Status)

@@

#potential code for EDA

@@

@@

```{r}
rawdata1%>%filter(grepl("Confirmed", Status))
unique(rawdata1$Food)
d2=rawdata1%>%
  filter(!is.na(Food))%>%
  mutate(Food=fct_lump(Food,10))%>%
  count(Food)%>%
  arrange(desc(n))
d2
d3=rawdata1%>%
  filter(!is.na(Species))%>%
  mutate(Food=fct_collapse(Food,Norovirus=c("Norovirus","Norovirus genogroup I","Norovirus genogroup II")))%>%
  mutate(Food=fct_lump(Species,10))%>%
  count(Species)%>%
  arrange(desc(n))
d3
```

>>>>

---
title: "Data Pre-Processing/Cleaning Script"
author: "Andreas Handel"
date: "2023-01-03"
output: html_document
---
# Load Libraries

```{r}
# General Pre-Processing
library(tidyverse)
library(dplyr)
library(stringr)

@@

```{r}
# Plot of NAs After Limiting to Analysis Data to Food
plot_na_pareto(analysis_data %>% filter(`Primary Mode` == "Food"))
```

## Checking Etiologies
```{r}
# Training Data
unique(training_data$Status)

@@

# checking the levels under each variable

:D

```{r}
skim(d1$Food)
#convert Food to factor
d1$Food=as.factor(d1$Food)
str(d1$Food)
#Since there are over 3000 different levels, we need to combine some food into the same category
d2=
```

checking the levels under `Species`
```{r}

```

# Checking the levels under `Location`
```{r}

```

@@

### Modifying IFSAC Category to Include Salads
```{r}
Desserts <- c("cookies", "cake", "chocolate", "brownie")

analysis_data_fin <- analysis_data_fin %>%
  mutate(`IFSAC Category` = case_when(
    grepl("Salad", `Food Vehicle`, ignore.case = TRUE) ~ "Salad",
    grepl(paste(Desserts, 
                collapse = "|"), `Food Vehicle`) ~ "Dessert",
    grepl("Chicken", `Food Vehicle`, ignore.case = TRUE) ~ "Poultry",
    grepl("Turkey", `Food Vehicle`, ignore.case = TRUE) ~ "Poultry",
    grepl("Poultry", `Food Vehicle`, ignore.case = TRUE) ~ "Poultry",
    TRUE ~ `IFSAC Category`))
```

@@

## Check Data Structure Again
```{r}
skim(analysis_data_fin)
```

```{r}
rawdata1%>%filter(grepl("Confirmed", Status))
food=rawdata1%>%
  filter(!is.na(Food))%>%
  group_by(Food)%>%
  top_n(n=10)
food
species=rawdata1%>%
  filter(!is.na(Species))%>%
  mutate(Species=fct_collapse(Species,Norovirus=c("Norovirus","Norovirus genogroup I","Norovirus genogroup II","Norovirus unknown")))%>%
  mutate(Species=fct_lump(Species,11,other_level = NA))%>%
  count(Species)%>%
  arrange(desc(n))%>%
  filter(!is.na(Species))
species
```
